|

### 2020-05-19 paper/Manuscript.Rmd
Add R for data science book

Although the principles underlying this workflow are universal, WORCS has been optimized for R [@rcoreteamLanguageEnvironmentStatistical2020].
Several arguments support the choice to work in R.
First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science.
Second, as of this writing, R is the most advanced programming language in terms of the implementation of tools required for an open science workflow.
Third, R is well-supported; a vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.

<!-- LB: Perhaps give some pointers to learn R (e.g. R4DataScience)-->
Third, at the time of writing, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, and output can be written to most file types, including DOCX and PDF (in APA style), and HTML format. 
Moreover, wrappers are available for many tools developed in other programming languages, and code written in other programming languages can be evaluated from R [including C++, Fortran, and Python, @allaireMarkdownPythonEngine].

>>>>

Although the principles underlying this workflow are universal, WORCS has been optimized for R [@rcoreteamLanguageEnvironmentStatistical2020].
Several arguments support the choice to work in R.
First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science.
Second, as of this writing, R is the most advanced programming language in terms of the implementation of tools required for an open science workflow.
Third, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Fourth, R is well-supported; a vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, and output can be written to most file types, including DOCX and PDF (in APA style), and HTML format. 
Moreover, wrappers are available for many tools developed in other programming languages, and code written in other programming languages can be evaluated from R [including C++, Fortran, and Python, @allaireMarkdownPythonEngine]. There are excellent free resources for learning R, such as the book R for Data Science [@grolemundDataScience2017].
